Perturbation theories in the complex plane

### 2020-06-29 SlideToulouse/main.tex
Add files via upload

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
\usepackage{mathpazo}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{multimedia}
\usepackage{subfigure}
\usepackage[absolute,overlay]{textpos}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}

@@

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering
Full Configuration Interaction gives access to high-order terms of the perturbation series!
\end{beamerboxesrounded}

@@

\begin{frame}{Deceptive or slow convergences}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

@@

\begin{frame}{Multi-reference and spin contamination}
\begin{table}
    \centering
    \begin{tabular}{c c c c c c c}
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\end{tabular}
    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set.}
    \label{tab:my_label}
\end{table}

\footnotetext{\tiny{Gill et al. Why does unrestricted M{\o}ller-Plesset perturbation theory converge so slowly for spin-contaminated wave functions, \textit{Journal of chemical physics}, 1988}}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{The-energy-corrections-for-HF-at-stretched-geometry-in-the-cc-pVDZ-basis.png}
    \caption{The energy corrections for HF at stretched geometry in the cc-pVDZ basis.}
    \label{fig:my_label}
\end{figure}

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

@@

\begin{frame}{A two-state model}

@@

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

@@

\begin{frame}{Two-state model}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figure-fig14.png}
    \caption{\centering The energy corrections for HF at stretched geometry in the aug'-cc-pVDZ basis with the two-state model.\textsuperscript{a}}
    \label{fig:my_label}
\end{figure}

\footnotetext{\tiny{Olsen et al. Divergence in Møller–Plesset theory: A simple explanation based on a two-state model, \textit{Journal of chemical physics}, 2000}}

@@

\begin{frame}{Existence of a critical point}

@@

\footnote{stillinger, sergeev, baker}

@@

\begin{frame}{Singularities $\alpha$ and $\beta$}

@@

\footnote{sergeev}

@@

\begin{frame}{Spherium: a theoretical playground}

>>>>

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{mathpazo}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{multimedia}
\usepackage[absolute,overlay]{textpos}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage[style=verbose,backend=bibtex]{biblatex}
\bibliography{SlideToulouse}

@@

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering

Full Configuration Interaction gives access to high-order terms of the perturbation series!

@@

\begin{frame}{Deceptive or slow convergences\footcite{gill_deceptive_1986}}

\begin{figure}
    \centering

    \includegraphics[width=0.45\textwidth]{gill1986.png}

    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

@@

\begin{frame}{Multi-reference and spin contamination\footcite{gill_why_1988}}
\begin{table}
    \centering
    \begin{tabular}{c c c c c c c}
\hline
 $r$ & UHF & UMP2 & UMP3 & UMP4 & $\expval{S^2}$ \\
\hline
0.75 & 0.0\% & 63.8\% & 87.4\% & 95.9\% & 0.00\\
1.35 & 0.0\% & 15.2\% & 26.1\% & 34.9\% & 0.49\\
2.00 & 0.0\% & 01.0\% & 01.8\% & 02.6\% & 0.95\\
2.50 & 0.0\% & 00.1\% & 00.3\% & 00.4\% & 0.99\\
\hline
\end{tabular}
    \caption{\centering Percentage of electron correlation energy recovered and $\expval{S^2}$ for the \ce{H2} molecule as a function of bond length (r,\si{\angstrom}) in the STO-3G basis set.}
    \label{tab:my_label}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{The-energy-corrections-for-HF-at-stretched-geometry-in-the-cc-pVDZ-basis.png}
    \caption{The energy corrections for HF at stretched geometry in the cc-pVDZ basis. \footcite{olsen_divergence_2000}}
    \label{fig:my_label}
\end{figure}

@@

\begin{frame}{A two-state model\footcite{olsen_divergence_2000}}

@@

@@

\begin{frame}{Two-state model\footcite{olsen_divergence_2000}}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figure-fig14.png}
    \caption{\centering The energy corrections for HF at stretched geometry in the aug'-cc-pVDZ basis with the two-state model.}
    \label{fig:my_label}
\end{figure}

@@

\begin{frame}{Existence of a critical point\footcite{stillinger_mollerplesset_2000}}

@@

@@

\begin{frame}{Singularities $\alpha$ and $\beta$ \footcite{sergeev_singularities_2006}}

@@

@@

\begin{frame}{Spherium: a theoretical playground\footcite{loos_ground_2009}}
